Machine Learning Methods for Discourse Segmentation of Communications in E-Mail Based Behavioral Interventions

### 2018-08-05 paper-amia-summit-2018/manuscript.tex
added footnote for GloVe word embeddings

Figure~\ref{fig:embedding-dimension-mlp} (left) illustrates the performance of CRNN model on e-Coaching email segmentation by varying the dimension of pre-trained and trained word embeddings with GloVe and word2vec models. It was observed that best performance achieved with pre-trained 300-dimensional word2vec word vectors when three types of features are used together. Therefore, we report our results with word2vec 300-dimensional word vectors for all deep learning models used in this study. For MLP models, the first layer input was prepared by the summation of first $l$ word vectors and last $l$ word vectors when a sample contains $2l$ words or punctuations. Figure~\ref{fig:embedding-dimension-mlp} (right) demonstrates the performance of MLP model on e-Coaching email segmentation by varying the value of $l$. It was observed that the best performance of MLP classifier is achieved when $l = 2$. Therefore, results of all MLP models are reported with $l = 2$.

>>>>

Figure~\ref{fig:embedding-dimension-mlp} (left) illustrates the performance of CRNN model on e-Coaching email segmentation by varying the dimension of pre-trained and trained word embeddings with GloVe\footnote{https://nlp.stanford.edu/projects/glove/} and word2vec models. It was observed that best performance achieved with pre-trained 300-dimensional word2vec word vectors when three types of features are used together. Therefore, we report our results with word2vec 300-dimensional word vectors for all deep learning models used in this study. For MLP models, the first layer input was prepared by the summation of first $l$ word vectors and last $l$ word vectors when a sample contains $2l$ words or punctuations. Figure~\ref{fig:embedding-dimension-mlp} (right) demonstrates the performance of MLP model on e-Coaching email segmentation by varying the value of $l$. It was observed that the best performance of MLP classifier is achieved when $l = 2$. Therefore, results of all MLP models are reported with $l = 2$.
